\LARGE \bf Multi-Armed Bandit Models for Sample-Based Grasp Planning in the Presence of Uncertainty [v-13 09-30-2014]

### 2014-10-02 paper.tex
Updated the references to focus on multi-armed bandits.

 Past work on grasping under uncertainty has focused on state uncertainty \cite{goldberg1990bayesian}, \cite{goldberg1990stochastic},  \cite{stulp2011learning},  uncertainty in object pose \cite{christopoulos2007handling},  \cite{felip2009robust}, \cite{kim2012physically} or uncertainty in the location of contact with the object \cite{zheng2005}. Robust grasp selection for parallel jaw grippers on uncertain shapes was studied by Kehoe et al. for both zero-slip push grasps \cite{kehoe2012toward} and slip push grasps \cite{kehoe2012estimating} using Monte Carlo integration for the expected grasp quality, but this approach was limited to polygonal shapes.  Christopoulo et al. sampled spline fits for 2-dimensional planar objects to measure the quality of uncertainty, however it is has not been shown how a spline based method could incorporate non-visual sensing information for representing shape uncertainty.

 The choice of using Gaussian Process Implicit Surfaces to represent uncertainty, is based on the fact it provides a formal way to include various sources of noise from observations such as tactile, laser and visual. Futhermore, implicit surface representations are becoming increasingly popular in robotics due to their success in real-time surface modeling from range images \cite{curless1996volumetric}, \cite{newcombe2011kinectfusion}, \cite{hornung2013octomap}. Some exciting work done with GPIS representation are the following: Hollinger et al. used GPIS to perform active sensing on the hulls in underwater boats \cite{hollinger2013}. Dragiev et al. showed how GPIS can represent shapes for grasps and used  as a grasp controller on the continuous signed distance function \cite{dragiev2011}. Mahler et al. used GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem \cite{jeff}.

  For grasp quality evaluation with shape uncertainty a common method involves sampling from the distribution on shape \cite{kehoe2012estimating},  \cite{kehoe2012toward}, \cite{christopoulos2007handling}. With GPIS this requires computationally intensive sampling from a signed distance field that is the dimension of the workspace. We propose an alternative distribution to sample from, based on the idea that we only need to consider the approach trajectory of the gripper.

Monte-Carlo integration involves drawing random samples from a distribution to approximate an integral \cite{caflisch1998monte}. While previous work has looked at quality evaluation of a single grasp with uncertainty \cite{christopoulos2007handling}, \cite{zheng2005}, few have compared many different grasps with uncertainty and efficiently chosen the best one.  Adaptive Sampling is the idea of allocating samples based on previous observations or rewards, which can be described as a multi-arm bandit problem \cite{barto1998reinforcement}. Prior work by Kehoe et al. \cite{kehoe2012toward} used an adaptive sampling approach that removed low quality grasps based on values received, but this method had no statistical guarantees and could lead to high quality grasps being removed. To achieve guarantees, we frame the problem as a "budgeted multi-arm bandit" problem, where exploration and exploitation are decoupled and the agent has to allocate resources to explore for a finite time then decide which arm to exploit  \cite{madani2004budgeted}. Drawing from the literature on Monte-Carlo sampling we estimate the confidence bounds of grasps and prune only those that are statistically distinguishable \cite{caflisch1998monte}.

>>>>

Past work on grasping under uncertainty has considered state uncertainty \cite{goldberg1990bayesian, stulp2011learning},  uncertainty in object pose \cite{christopoulos2007handling, weisz2012pose, kim2012physically}, or uncertainty in contact locations with an object \cite{zheng2005}.
The effect of uncertainty in object geometry on grasp selectiong has been studied for spline representations of objects~\cite{christopoulos2007handling}, extruded polygonal mesh models~\cite{kehoe2012estimating, kehoe2012toward}, and point clouds~\cite{hsiao2011bayesian}.

Currently, the most common method of evaluating grasp quality under shape and pose uncertainty is to rank a set of random grasps on an object using Monte-Carlo integration on shape and / or pose samples to evaluate a quality measure~\cite{christopoulos2007handling, kehoe2012estimating, kehoe2012toward}.
Monte-Carlo integration involves drawing random samples from a distribution to approximate an integral \cite{caflisch1998monte}, which can be slow when the distribution is high-dimensional, such as for distributions on possible shape.
To address this, Kehoe et al.~\cite{kehoe2012estimating, kehoe2012toward} demonstrated a procedure for finding a minumum bound on grasp quality given shape uncertainty, which reduced the number of terms needed in Monte-Carlo integration in order to rank grasps, but the method could potentially remove high quality grasps.
Laaksonen et al.~\cite{laaksonen2012probabilistic} used Markov Chain Monte Carlo (MCMC) sampling to estimate grasp stability and object pose online under shape and pose uncertainty.
MCMC simplified sampling from complicated distributions on pose and shape, but it can be slow to converge to the correct distribution~\cite{andrieu2003introduction}.

The multi-armed bandit problem~\cite{barto1998reinforcement, lai1985asymptotically, robbins1985some} is to maximize the total expected reward over a sequence of possible choices over a set of competing options, each of which has a probablistic reward function.
The optimal sequence of choices if the rewards are known is to always pick the option with the maximum expected reward over the set of possible options.
However, to discover which choice is optimal requires a balance between exploration, or choosing options that are not well known, and exploitation, or choosing the current `best' option~\cite{barto1998reinforcement}.
Solutions to this problem, called {\it policies}, include choosing the next option based on Thompson sampling~\cite{agrawal2011analysis}, the Gittins index policy~\cite{weber1992gittins}, and by using an upper confidence bound (UCB) for the expected reward of each option~\cite{auer2002finite}.
The UCB can be computed from the sample mean~\cite{agrawal1995sample}, Kullback-Leibler divergence~\cite{cappe2013kullback}, or a prior on the rewards~\cite{kaufmann2012bayesian}.
Solutions to the multi-armed bandit problem are well suited to applications for which it is expensive to exhaustively evaluate all possible options, and therefore these methods have been applied to optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.

In this paper we consider the "budgeted multi-arm bandit" problem, where exploration and exploitation are decoupled and the agent can only explore for a finite time before deciding which arm to exploit~\cite{madani2004budgeted}.

We study using Gaussian process implicit surfaces (GPIS) to represent shape uncertainty, based on its ability to combine various modes of nois observations such as tactile, laser and visual.
GPIS representations model a distribution over implicit surface functions, which are becoming increasingly popular in robotics due to their success in real-time surface modeling from range images \cite{curless1996volumetric, newcombe2011kinectfusion}.
GPIS representations have recently been used in a number of robotic appications.
Hollinger et al. used GPIS to perform active sensing on the hulls in underwater boats \cite{hollinger2013}.
Dragiev et al. showed how GPIS can represent shapes for grasps and used  as a grasp controller on the continuous signed distance function \cite{dragiev2011}.
Mahler et al. used GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem \cite{jeff}. 
Sampling from GPIS for grasp quality evaluation is computationally intensive, however, because it involves the Cholesky decomposition of an $m \times m$ matrix which takes $O(m^6)$ time, where $m$ is the dimension for a 2D grid over and object \cite{morrison1990multivariate}.
